Explaining the reportedly over-massive black holes in early-type galaxies with intermediate-scale discs

### 2015-11-18 papers/ellicular/arxiv/ellicular.tex
victory

%\title[Non over-massive black holes in early-type galaxies]{Early-type galaxies with intermediate-scale discs and their (non over-massive) black holes}
\title[Explaining the reportedly over-massive black holes]
{Explaining the reportedly over-massive black holes in early-type galaxies with intermediate-scale discs}

\author[G.~A.~D. Savorgnan \& A.~W. Graham]
{\parbox{\textwidth}{
Giulia~A.~D. Savorgnan$^{1}$\thanks{E-mail: \texttt{gsavorgn@astro.swin.edu.au}},
Alister W. Graham$^{1}$}\vspace{0.4cm}\\
\parbox{\textwidth}{
$^{1}$Centre for Astrophysics and Supercomputing, Swinburne University of Technology, Hawthorn, Victoria 3122, Australia.\\}}

@@

\begin{abstract}
{\bf The classification ``early-type'' galaxy includes both elliptically- and lenticular-shaped galaxies. 
Theoretically, the spheroid-to-disc flux ratio of an early-type galaxy can assume any positive value,  
but in practice studies often consider only spheroid/disc decompositions 
in which the disc neatly dominates over the spheroid at large galaxy radii, 
creating an inner ``bulge'' as observed in most spiral galaxies. 
Here we show that decompositions in which the disc remains embedded within the spheroid, 
labelled by some as ``unphysical'',  
correctly reproduce both the photometric and kinematic properties of early-type galaxies 
with intermediate-scale discs. 
Intermediate-scale discs have often been confused with large-scale discs and incorrectly modelled as such; 
when this happens, the spheroid luminosity is considerably underestimated. 
This has recently led to some surprising conclusions, 
such as the claim that a number of galaxies with intermediate-scale discs (Mrk 1216, NGC 1277, NGC 1271, and NGC 1332) 
host a central black hole whose mass is abnormally large compared to expectations from the (underestimated) spheroid luminosity. 
We show that when these galaxies are correctly modelled, 
they no longer appear as extreme outliers in the (black hole mass)-(spheroid mass) diagram. 
This not only nullifies the need for invoking different evolutionary scenarios for these galaxies 
but it strengthens the significance of the observed (black hole mass)-(spheroid mass) correlation 
and confirms its importance as a fundamental ingredient for theoretical and semi-analytic models 
used to describe the coevolution of spheroids and their central supermassive black holes. }

@@

{\bf The awareness that \emph{many} early-type galaxies contain previously over-looked stellar discs dates back half a century 

@@

%A specific angular momentum profile that is rapidly increasing beyond 1--2 half-light radii 
%is a signature of a large-scale disc, 
%while a specific angular momentum profile that increases up to 1--2 half-light radii and then declines beyond that point 
%indicates the presence of an intermediate-scale disc that no longer dominates at large radii. 

@@

Finally, in Section \ref{sec:disc} we briefly discuss our results in terms of galaxy evolution. }

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{discmodel.eps}
\caption{Illustration of the spheroid/disc decomposition of the one-dimensional surface brightness profile, $\mu$, 
the ellipticity profile, $\epsilon$, and the specific angular momentum profile, $\lambda$,
for the three prototype early-type galaxy sub-classes. 
In the flux decompositions, the spheroid (or bulge) and the disc are shown with the red and blue color, respectively. 
The left panel shows a disc-dominated central fast rotator (lenticular galaxy), composed of a bulge encased in a large-scale disc. 
The right panel displays a spheroid-dominated slow rotator (elliptical) with (an optional) nuclear stellar disc. 
The middle panel presents a spheroid-dominated central fast rotator with an intermediate-sized disc embedded in the spheroid. }
\label{fig:model}
\end{center}
\end{figure}

\section{Intermediate-scale disc galaxies}
\label{sec:gal}
Three examples of galaxies with intermediate-scale discs are Mrk 1216, NGC 1332, and NGC 3115. 
In the following Section, we present a photometric analysis of these three galaxies, 
and we compare our results with the kinematical analysis available from the literature for Mrk 1216 and NGC 3115. 
For the galaxies NGC 1332 and NGC 3115, we used $3.6~\rm \mu m$ images obtained with the InfraRed Array Camera (IRAC) 
onboard the \emph{Spitzer Space Telescope}. 
For the galaxy Mrk 1216, we used an archived Hubble Space Telescope (\emph{HST}) image  
taken with the Wide Field Camera 3 (WFC3) and the near-infrared \emph{F160W} filter ($H$-band). 
Our galaxy decomposition technique is extensively described in Savorgnan \& Graham (2015).
Briefly, the galaxy images were background-subtracted, and masks for contaminating sources were created. 
The one-dimensional Point Spread Function (PSF) was characterized using a Gaussian profile for the \emph{HST} observation 
and a \cite{moffat1969} profile for the \emph{Spitzer} observations.
We performed an isophotal analysis of the galaxies using the IRAF\footnote{IRAF 
is the Image Reduction and Analysis Facility, distributed by the National Optical Astronomy Observatory, 
which is operated by the Association of Universities for Research in Astronomy (AURA) 
under cooperative agreement with the National Science Foundation.} task {\tt ellipse}\footnote{Our analysis 
was performed before {\tt isofit} \citep{ciambur2015} was conceived or available. 
After {\tt isofit} was recently developed and implemented in IRAF, 
we employed it to re-extract the surface brightness profiles of the galaxies NGC 1332 and NGC 3115. 
We then repeated the analysis and checked that this change does not significantly alter our results. 
In fact, although {\tt isofit} provides a more accurate description of the isophotes in the presence of an inclined disc, 
the discs of NGC 1332 and NGC 3115 are relatively faint compared to the spheroidal components, 
therefore the differences between the light profile obtained with {\tt ellipse} and that obtained with {\tt isofit} 
are small for these two galaxies. } 
\citep{taskellipse}. 
The galaxy isophotes were modelled with a series of concentric ellipses, 
allowing the ellipticity, the position angle and the amplitude of the fourth harmonic to vary with radius.  
The decomposition of the surface brightness profiles was performed with software written by G. Savorgnan 
and described in Savorgnan \& Graham (2015).
We modelled the light profiles with a combination of PSF-convolved analytic functions, 
using one function per galaxy component.

\subsection{NGC 3115}
The presence of a disc in the {\bf central fast rotator} NGC 3115 
{\bf (e.g.~\citealt{strom1977,nieto1988,scorzabender1995}) }
is obvious due to its edge-on orientation (Figure \ref{fig:n3115}). 
Less obvious is the radial extent of this disc if one only relies on a visual inspection of the galaxy image. 
The ellipticity profile (Figure \ref{fig:n3115}) is consistent with the presence of an intermediate-scale disc. 
Moreover, the kinematics of NGC 3115 \citep{arnold2011n3115} also disprove the presence of a large-scale disc, 
because the galaxy is rapidly rotating only within two galaxy half-light radii ($\sim 2 \times 50~\rm arcsec$), 
and the rotation significantly drops at larger radii.  
The unsharp mask of NGC 3115 (Figure \ref{fig:n3115}) betrays the presence of a faint edge-on nuclear ring, 
which can also be spotted as a small peak in the ellipticity profile 
(at semi-major axis length $R_{\rm maj} \sim 15~\rm arcsec$). 
Such rings are common in early-type galaxies (e.g.~\citealt{michardmarchal1993}).
The spheroidal component of NGC 3115 is well described with a \cite{sersic1963} profile.
The highly inclined intermediate-scale disc is better fit with an $n<1$ S\'ersic profile 
(the S\'ersic index $n$ regulates the curvature of the S\'ersic profile) 
rather than with an exponential function, 
as explained by \cite{pastrav2013a}. 
The nuclear ring is modelled with a Gaussian function. \\
In comparison, \cite{lasker2014data} fit NGC 3115 with a bulge + disc + envelope, 
and measured a bulge half-light radius of $3.9~\rm arcsec$ and a bulge-to-total ratio of $0.12$. 
We describe this galaxy using a spheroid + intermediate-scale disc + nuclear ring, 
and obtain a spheroid half-light radius of $43.6~\rm arcsec$ and a spheroid-to-total ratio of $0.85$. 
We have used both kinematical information and ellipticity profiles, 
together with the surface brightness profile, 
to obtain a physically consistent and meaningful model.

@@

\subsection{Mrk 1216}
Although the disc in the {\bf central fast rotator} Mrk 1216 is not immediately apparent from the image (Figure \ref{fig:m1216}), 
the velocity map \citep{yildirim2015} reveals the presence of a fast rotating component 
within three galaxy half-light radii ($\sim 3 \times 5~\rm arcsec$). 
The ellipticity profile (Figure \ref{fig:m1216}), 
which extends out to five half-light radii, indicates the presence of an intermediate-scale disc. 
In addition, a nuclear disc is identified from the change in slope of the ellipticity profile ($R_{\rm maj} \sim 1 - 2 \rm~arcsec$), 
from the unsharp mask, 
and from a clear feature in the $B4$ fourth harmonic profile (not shown here). 
We modelled the surface brightness profile of Mrk 1216 (Figure \ref{fig:m1216}) with a S\'ersic-spheroid, 
an intermediate-sized exponential-disc, and a nuclear exponential-disc.

\subsection{Other galaxies}
Our models with an intermediate-sized disc embedded within a larger spheroidal component, 
plus an additional nuclear component when one is present, 
match the observed light distribution, and explain both the extended kinematic maps (when available, \citealt{arnold2014}) and the ellipticity profiles, 
of five additional galaxies for which a direct measurement of their central supermassive black hole mass is available: 
NGC 821; NGC 1271; NGC 1277; NGC 3377; and NGC 4697. 
Our isophotal analysis and galaxy decompositions for NGC 1271 and NGC 1277 will be presented in 
Graham, Savorgnan \& Ciambur (\emph{in prep.}) and Graham et al.~(2015), respectively, 
while the galaxies NGC 821, NGC 3377 and NGC 4697 have been analysed in Savorgnan \& Graham (2015).

\subsubsection{NGC 1271}
\cite{walsh2015} explored a three-component decomposition for the {\bf central fast rotator} NGC 1271 
and identified the galaxy bulge with the innermost of the three components, 
having a half-light radius of $0.61~\rm arcsec$ and a bulge-to-total flux ratio of $0.23$; 
our model features a spheroid + intermediate-scale disc, 
with a spheroid half-light radius of $3.3~\rm arcsec$ and a spheroid-to-total flux ratio of $0.67$.

\subsubsection{NGC 1277}
\cite{vandenbosch2012} proposed a model for the {\bf central fast rotator} NGC 1277 with a bulge + disc + nuclear source + envelope, 
which gives a bulge half-light radius of $0.9~\rm arcsec$ and a bulge-to-total flux ratio of $0.24$; 
our model consists of a spheroid + intermediate-scale disc + nuclear component, 
and produces a spheroid half-light radius of $6.0~\rm arcsec$ and a spheroid-to-total flux ratio of $0.79$.

\subsubsection{NGC 3377}
\cite{lasker2014data} modelled the {\bf central fast rotator} NGC 3377 
{\bf (e.g.~\citealt{jedrzejewski1987inproceedings,scorzabender1995}) }
with a bulge + nuclear disc + disc + envelope, 
and obtained a bulge half-light radius of $10.1~\rm arcsec$ and a bulge-to-total flux ratio of $0.35$; 
our model with a spheroid + intermediate-scale disc + nuclear disc 
returns a spheroid half-light radius of $61.8~\rm arcsec$ and a spheroid-to-total flux ratio of $0.94$.

\subsubsection{NGC 821}
\cite{lasker2014data} decomposed the {\bf central fast rotator} NGC 821 into a bulge + disc + envelope, 
and measured a bulge half-light radius of $3.8~\rm arcsec$ and a bulge-to-total flux ratio of $0.19$; 
our decomposition consists of a spheroid + intermediate-scale disc, 
with a spheroid half-light radius of $36.5~\rm arcsec$ and a spheroid-to-total flux ratio of $0.79$.

\subsubsection{NGC 4697}
{\bf While NGC 4697 (e.g.~\citealt{carter1987,Jedrzejewski1987n720n1052n4697,davies1981}) 
was explicitly referred to as a ``fast rotator'' by \cite{capaccioli1987} and \cite{petrou1981}, 
it is only a central fast rotator} and it represents an ``extreme'' case. 
\cite{lasker2014data} fit this galaxy with a bulge + nuclear source + disc + envelope, 
and obtained a bulge half-light radius of $6.3~\rm arcsec$ and a bulge-to-total flux ratio of $0.08$; 
we described NGC 4697 using a spheroid + intermediate-scale disc + nuclear disc model, 
and measured a spheroid half-light radius of $239.3~\rm arcsec$ and a spheroid-to-total flux ratio of $0.89$. \\

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.49\columnwidth]{n3115_image.jpeg}
\includegraphics[width=0.49\columnwidth]{n3115_unsharp.jpeg} \\
\includegraphics[width=1.05\columnwidth]{n3115_decomposition.pdf}
\caption{NGC 3115. 
The top panels are the \emph{Spitzer}/IRAC $3.6~\rm \mu m$ image (left) and its unsharp mask (right), 
obtained by dividing the image by a Gaussian-smoothed version of itself. 
The bottom plots display the best-fit model of the surface brightness profile, $\mu$, 
and the ellipticity profile, $\epsilon$, 
along the major-axis, $R_{\rm maj}$. 
The black points are the observed data, which extend out to five galaxy half-light radii ($\sim 5 \times 50~\rm arcsec$). 
The color lines represent the individual (PSF-convolved) model components: 
{\bf red solid = S\'ersic (spheroid), blue dashed = S\'ersic (disc), green dotted = Gaussian ring. }
The residual profile (data $-$ model) is shown as $\Delta \mu$. 
The horizontal gray dashed line corresponds to an intensity equal to three times the root mean square of the sky background fluctuations. 
$\Delta$ denotes the root mean square scatter of the fit in units of $\rm mag~arcsec^{-2}$. }
\label{fig:n3115}
\end{center}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.49\columnwidth]{mrk1216_image.jpeg}
\includegraphics[width=0.49\columnwidth]{mrk1216_unsharp.jpeg} \\
\includegraphics[width=1.05\columnwidth]{mrk1216_decomposition.pdf}
\caption{Mrk 1216. 
Similar to Figure \ref{fig:n3115}. 
The top panels are the \emph{HST}/WFC3 \emph{F160W} image (left) and its unsharp mask (right).
The surface brightness profile extends out to five galaxy half-light radii ($\sim 5 \times 5~\rm arcsec$). 
The color lines represent the individual (PSF-convolved) model components:
{\bf red solid = S\'ersic (spheroid), blue dashed = exponential (nuclear and intermediate-scale disc). }
}
\label{fig:m1216}
\end{center}
\end{figure}

@@

Savorgnan et al.~(2015) shows that, when considering all galaxies irrespective of their morphological type, 

@@

(Savorgnan et al.~2015). 

@@

for early-type galaxies from Savorgnan et al.~(2015). 

@@

and extensively described in Savorgnan \& Graham (2015). 

@@

Acknowledging the correct structure of galaxies with intermediate-scale discs is important to properly understand their origin. 
According to the current paradigm of cosmological structure evolution, 
the genesis of massive early-type galaxies is characterized by two distinct phases: ``in-situ'' and ``ex-situ''. 
The first phase takes place in a young Universe (within its first $4~\rm Gyr$), 
when cold gas inflows produced short and intense bursts of star formation 
that created compact and dense conglomerates of stars with high velocity dispersion (e.g.~\citealt{prieto2013}). 
These naked and compact conglomerates, named ``red nuggets'' \citep{damjanov2009}, 
have been observed at high-redshift with half-light sizes of 1--2 kpc \citep{daddi2005,trujillo2006,vandokkum2008}.
In the second phase (last $10~\rm Gyr$), discs and stellar envelopes 
were accreted around these primordial conglomerates and the external parts of today's galaxies assembled on scales of 2--20 kpc 
(e.g.~\citealt{driver2013}). \\
Today's Universe is populated by an abundance of compact, massive spheroids, 
with the same physical properties -- mass and compactness -- as the high-redshift red nuggets \citep{GDS2015}. 
Some of these local compact massive spheroids are encased within a large-scale disc, 
that is to say they are the bulges of some lenticular and spiral galaxies.  
Over the last $10~\rm Gyr$ their spheroids have evolved by growing a relatively flat disc (e.g.~\citealt{pichon2011,danovich2012,stewart2013})
-- rather than a three-dimensional envelope -- 
which has increased the galaxy size but preserved the bulge compactness. 
{\bf Of course some lenticular/ES galaxies may have been built from mergers (e.g.~\citealt{querejeta2015}, and references therein). }
The other compact massive spheroids of today's Universe belong to some galaxies with intermediate-scale discs. 
Indeed, Mrk 1216, NGC 1271, NGC 1277, NGC 1332, and NGC 3115 are all local compact intermediate-scale disc galaxies 
with purely old ($>10~\rm Gyr$) stellar populations. 
These galaxies have undergone the lowest degree of disc growth. \\
In addition to the observational clues as to the actual physical components in galaxies with intermediate-scale discs, 
one can reason on other grounds as to why these compact galaxies are not comprised of an inner bulge 
plus large-scale disc plus outer envelope. 
If they were such three-component systems, then one would have two possibilities. 
The first possibility is that these galaxies were already fully assembled $10~\rm Gyr$ ago; 
this would explain their old stellar populations, 
but it would also imply that their discs and envelopes had already formed during the first $4~\rm Gyr$ of the Universe, 
in disagreement with the current cosmological picture. 
The second possibility is that only their inner bulges (with sizes of 0.1--0.2 kpc, 
according to past decompositions) originated in the first $4~\rm Gyr$ 
and they subsequently accreted a substantial disc and envelope. 
If this was correct, then we would observe high-redshift, star-like, naked bulges with stellar masses 
within a factor of a few times the currently observed red nuggets but sizes which are $10$ times smaller. 
However, a dramatically different expectation is reached 
if one considers these galaxies today as spheroid-dominated systems with an intermediate-scale disc; 
in this case, both the galaxy size and the spheroid size are compact (1--2 kpc). 
This implies that, among the local descendants of the high-redshift red nuggets, 
the compact intermediate-scale disc galaxies have undergone the lowest degree of disc growth. 
That is, the bulk of a compact intermediate-scale disc galaxy quickly assembled ``in-situ'' in a very young Universe 
and experienced very little evolution over the last $10~\rm Gyr$.

>>>>

\title[Explaining the reportedly over-massive black holes]
{Explaining the reportedly over-massive black holes in early-type galaxies with intermediate-scale discs}

\author[G.~A.~D. Savorgnan \& A.~W. Graham]
{\parbox{\textwidth}{
Giulia A.~D.~Savorgnan$^{1}$\thanks{E-mail: \texttt{gsavorgn@astro.swin.edu.au}},
Alister W.~Graham$^{1}$}\vspace{0.4cm}\\
\parbox{\textwidth}{
$^{1}$Centre for Astrophysics and Supercomputing, Swinburne University of Technology, Hawthorn, Victoria 3122, Australia.\\}}

@@

\begin{abstract}
The classification ``early-type'' galaxy includes both elliptically- and lenticular-shaped galaxies. 
Theoretically, the spheroid-to-disc flux ratio of an early-type galaxy can assume any positive value,  
but in practice studies often consider only spheroid/disc decompositions 
in which the disc neatly dominates over the spheroid at large galaxy radii, 
creating an inner ``bulge'' as observed in most spiral galaxies. 
Here we show that decompositions in which the disc remains embedded within the spheroid, 
labelled by some as ``unphysical'',  
correctly reproduce both the photometric and kinematic properties of early-type galaxies 
with intermediate-scale discs. 
Intermediate-scale discs have often been confused with large-scale discs and incorrectly modelled as such; 
when this happens, the spheroid luminosity is considerably underestimated. 
This has recently led to some surprising conclusions, 
such as the claim that a number of galaxies with intermediate-scale discs (Mrk 1216, NGC 1277, NGC 1271, and NGC 1332) 
host a central black hole whose mass is abnormally large compared to expectations from the (underestimated) spheroid luminosity. 
We show that when these galaxies are correctly modelled, 
they no longer appear as extreme outliers in the (black hole mass)-(spheroid mass) diagram. 
This not only nullifies the need for invoking different evolutionary scenarios for these galaxies 
but it strengthens the significance of the observed (black hole mass)-(spheroid mass) correlation 
and confirms its importance as a fundamental ingredient for theoretical and semi-analytic models 
used to describe the coevolution of spheroids and their central supermassive black holes.

@@

The awareness that \emph{many} early-type galaxies contain previously over-looked stellar discs dates back half a century 

@@

@@

Finally, in Section \ref{sec:disc} we briefly discuss our results in terms of galaxy evolution.

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{discmodel.pdf}
\caption{Illustration of the spheroid/disc decomposition of the one-dimensional surface brightness profile, $\mu$, 
the ellipticity profile, $\epsilon$, and the specific angular momentum profile, $\lambda$,
for the three prototype early-type galaxy sub-classes. 
In the flux decompositions, the spheroid (or bulge) and the disc are shown with the red and blue color, respectively. 
The left panel shows a disc-dominated central fast rotator (lenticular galaxy), composed of a bulge encased in a large-scale disc. 
The right panel displays a spheroid-dominated slow rotator (elliptical) with (an optional) nuclear stellar disc. 
The middle panel presents a spheroid-dominated central fast rotator with an intermediate-sized disc embedded in the spheroid. }
\label{fig:model}
\end{center}
\end{figure}

\section{Intermediate-scale disc galaxies}
\label{sec:gal}
Three examples of galaxies with intermediate-scale discs are Mrk 1216, NGC 1332, and NGC 3115. 
In the following Section, we present a photometric analysis of these three galaxies, 
and we compare our results with the kinematical analysis available from the literature for Mrk 1216 and NGC 3115. 
For the galaxies NGC 1332 and NGC 3115, we used $3.6~\rm \mu m$ images obtained with the InfraRed Array Camera (IRAC) 
onboard the \emph{Spitzer Space Telescope}. 
For the galaxy Mrk 1216, we used an archived Hubble Space Telescope (\emph{HST}) image  
taken with the Wide Field Camera 3 (WFC3) and the near-infrared \emph{F160W} filter ($H$-band). 
Our galaxy decomposition technique is extensively described in \cite{paperI}.
Briefly, the galaxy images were background-subtracted, and masks for contaminating sources were created. 
The one-dimensional Point Spread Function (PSF) was characterized using a Gaussian profile for the \emph{HST} observation 
and a \cite{moffat1969} profile for the \emph{Spitzer} observations.
We performed an isophotal analysis of the galaxies using the IRAF\footnote{IRAF 
is the Image Reduction and Analysis Facility, distributed by the National Optical Astronomy Observatory, 
which is operated by the Association of Universities for Research in Astronomy (AURA) 
under cooperative agreement with the National Science Foundation.} task {\tt ellipse}\footnote{Our analysis 
was performed before {\tt isofit} \citep{ciambur2015} was conceived or available. 
After {\tt isofit} was recently developed and implemented in IRAF, 
we employed it to re-extract the surface brightness profiles of the galaxies NGC 1332 and NGC 3115. 
We then repeated the analysis and checked that this change does not significantly alter our results. 
In fact, although {\tt isofit} provides a more accurate description of the isophotes in the presence of an inclined disc, 
the discs of NGC 1332 and NGC 3115 are relatively faint compared to the spheroidal components, 
therefore the differences between the light profile obtained with {\tt ellipse} and that obtained with {\tt isofit} 
are small for these two galaxies. } 
\citep{taskellipse}. 
The galaxy isophotes were modelled with a series of concentric ellipses, 
allowing the ellipticity, the position angle and the amplitude of the fourth harmonic to vary with radius.  
The decomposition of the surface brightness profiles was performed with software written by G. Savorgnan 
and described in \cite{paperI}.
We modelled the light profiles with a combination of PSF-convolved analytic functions, 
using one function per galaxy component.

\subsection{NGC 3115}
The presence of a disc in the central fast rotator NGC 3115 
(e.g.~\citealt{strom1977,nieto1988,scorzabender1995}) 
is obvious due to its edge-on orientation (Figure \ref{fig:n3115}). 
Less obvious is the radial extent of this disc if one only relies on a visual inspection of the galaxy image. 
The ellipticity profile (Figure \ref{fig:n3115}) is consistent with the presence of an intermediate-scale disc. 
Moreover, the kinematics of NGC 3115 \citep{arnold2011n3115} also disprove the presence of a large-scale disc, 
because the galaxy is rapidly rotating only within two galaxy half-light radii ($\sim 2 \times 50~\rm arcsec$), 
and the rotation significantly drops at larger radii.  
The unsharp mask of NGC 3115 (Figure \ref{fig:n3115}) betrays the presence of a faint edge-on nuclear ring, 
which can also be spotted as a small peak in the ellipticity profile 
(at semi-major axis length $R_{\rm maj} \sim 15~\rm arcsec$). 
Such rings are common in early-type galaxies (e.g.~\citealt{michardmarchal1993}).
The spheroidal component of NGC 3115 is well described with a \cite{sersic1963} profile.
The highly inclined intermediate-scale disc is better fit with an $n<1$ S\'ersic profile 
(the S\'ersic index $n$ regulates the curvature of the S\'ersic profile) 
rather than with an exponential function, 
as explained by \cite{pastrav2013a}. 
The nuclear ring is modelled with a Gaussian function. \\
In comparison, \cite{lasker2014data} fit NGC 3115 with a bulge + disc + envelope, 
and measured a bulge half-light radius of $3.9~\rm arcsec$ and a bulge-to-total ratio of $0.12$. 
We describe this galaxy using a spheroid + intermediate-scale disc + nuclear ring, 
and obtain a spheroid half-light radius of $43.6~\rm arcsec$ and a spheroid-to-total ratio of $0.85$. 
We have used both kinematical information and ellipticity profiles, 
together with the surface brightness profile, 
to obtain a physically consistent and meaningful model.

@@

\subsection{Mrk 1216}
Although the disc in the central fast rotator Mrk 1216 is not immediately apparent from the image (Figure \ref{fig:m1216}), 
the velocity map \citep{yildirim2015} reveals the presence of a fast rotating component 
within three galaxy half-light radii ($\sim 3 \times 5~\rm arcsec$). 
The ellipticity profile (Figure \ref{fig:m1216}), 
which extends out to five half-light radii, indicates the presence of an intermediate-scale disc. 
In addition, a nuclear disc is identified from the change in slope of the ellipticity profile ($R_{\rm maj} \sim 1 - 2 \rm~arcsec$), 
from the unsharp mask, 
and from a clear feature in the $B4$ fourth harmonic profile (not shown here). 
We modelled the surface brightness profile of Mrk 1216 (Figure \ref{fig:m1216}) with a S\'ersic-spheroid, 
an intermediate-sized exponential-disc, and a nuclear exponential-disc.

\subsection{Other galaxies}
Our models with an intermediate-sized disc embedded within a larger spheroidal component, 
plus an additional nuclear component when one is present, 
match the observed light distribution, and explain both the extended kinematic maps (when available, \citealt{arnold2014}) and the ellipticity profiles, 
of five additional galaxies for which a direct measurement of their central supermassive black hole mass is available: 
NGC 821; NGC 1271; NGC 1277; NGC 3377; and NGC 4697. 
Our isophotal analysis and galaxy decompositions for NGC 1271 and NGC 1277 will be presented in 
Graham, Savorgnan \& Ciambur (\emph{in prep.}) and \cite{graham2015n1277}, respectively, 
while the galaxies NGC 821, NGC 3377 and NGC 4697 have been analysed in \cite{paperI}.

\subsubsection{NGC 1271}
\cite{walsh2015} explored a three-component decomposition for the central fast rotator NGC 1271 
and identified the galaxy bulge with the innermost of the three components, 
having a half-light radius of $0.61~\rm arcsec$ and a bulge-to-total flux ratio of $0.23$; 
our model features a spheroid + intermediate-scale disc, 
with a spheroid half-light radius of $3.3~\rm arcsec$ and a spheroid-to-total flux ratio of $0.67$.

\subsubsection{NGC 1277}
\cite{vandenbosch2012} proposed a model for the central fast rotator NGC 1277 with a bulge + disc + nuclear source + envelope, 
which gives a bulge half-light radius of $0.9~\rm arcsec$ and a bulge-to-total flux ratio of $0.24$; 
our model consists of a spheroid + intermediate-scale disc + nuclear component, 
and produces a spheroid half-light radius of $6.0~\rm arcsec$ and a spheroid-to-total flux ratio of $0.79$.

\subsubsection{NGC 3377}
\cite{lasker2014data} modelled the central fast rotator NGC 3377 
(e.g.~\citealt{Jedrzejewski1987INPROCEEDINGS,scorzabender1995}) 
with a bulge + nuclear disc + disc + envelope, 
and obtained a bulge half-light radius of $10.1~\rm arcsec$ and a bulge-to-total flux ratio of $0.35$; 
our model with a spheroid + intermediate-scale disc + nuclear disc 
returns a spheroid half-light radius of $61.8~\rm arcsec$ and a spheroid-to-total flux ratio of $0.94$.

\subsubsection{NGC 821}
\cite{lasker2014data} decomposed the central fast rotator NGC 821 into a bulge + disc + envelope, 
and measured a bulge half-light radius of $3.8~\rm arcsec$ and a bulge-to-total flux ratio of $0.19$; 
our decomposition consists of a spheroid + intermediate-scale disc, 
with a spheroid half-light radius of $36.5~\rm arcsec$ and a spheroid-to-total flux ratio of $0.79$.

\subsubsection{NGC 4697}
While NGC 4697 (e.g.~\citealt{carter1987,Jedrzejewski1987n720n1052n4697,davies1981}) 
was explicitly referred to as a ``fast rotator'' by \cite{capaccioli1987} and \cite{petrou1981}, 
it is only a central fast rotator and it represents an ``extreme'' case. 
\cite{lasker2014data} fit this galaxy with a bulge + nuclear source + disc + envelope, 
and obtained a bulge half-light radius of $6.3~\rm arcsec$ and a bulge-to-total flux ratio of $0.08$; 
we described NGC 4697 using a spheroid + intermediate-scale disc + nuclear disc model, 
and measured a spheroid half-light radius of $239.3~\rm arcsec$ and a spheroid-to-total flux ratio of $0.89$. \\

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.49\columnwidth]{n3115_image.jpeg}
\includegraphics[width=0.49\columnwidth]{n3115_unsharp.jpeg} \\
\includegraphics[width=1.05\columnwidth]{n3115_decomposition.pdf}
\caption{NGC 3115. 
The top panels are the \emph{Spitzer}/IRAC $3.6~\rm \mu m$ image (left) and its unsharp mask (right), 
obtained by dividing the image by a Gaussian-smoothed version of itself. 
The bottom plots display the best-fit model of the surface brightness profile, $\mu$, 
and the ellipticity profile, $\epsilon$, 
along the major-axis, $R_{\rm maj}$. 
The black points are the observed data, which extend out to five galaxy half-light radii ($\sim 5 \times 50~\rm arcsec$). 
The color lines represent the individual (PSF-convolved) model components: 
red solid = S\'ersic (spheroid), blue dashed = S\'ersic (disc), green dotted = Gaussian ring. 
The residual profile (data $-$ model) is shown as $\Delta \mu$. 
The horizontal gray dashed line corresponds to an intensity equal to three times the root mean square of the sky background fluctuations. 
$\Delta$ denotes the root mean square scatter of the fit in units of $\rm mag~arcsec^{-2}$. }
\label{fig:n3115}
\end{center}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.49\columnwidth]{mrk1216_image.jpeg}
\includegraphics[width=0.49\columnwidth]{mrk1216_unsharp.jpeg} \\
\includegraphics[width=1.05\columnwidth]{mrk1216_decomposition.pdf}
\caption{Mrk 1216. 
Similar to Figure \ref{fig:n3115}. 
The top panels are the \emph{HST}/WFC3 \emph{F160W} image (left) and its unsharp mask (right).
The surface brightness profile extends out to five galaxy half-light radii ($\sim 5 \times 5~\rm arcsec$). 
The color lines represent the individual (PSF-convolved) model components:
red solid = S\'ersic (spheroid), blue dashed = exponential (nuclear and intermediate-scale disc). 
}
\label{fig:m1216}
\end{center}
\end{figure}

@@

\cite{paperII} shows that, when considering all galaxies irrespective of their morphological type, 

@@

\citep{paperII}. 

@@

for early-type galaxies from \cite{paperII}. 

@@

and extensively described in \cite{paperI}. 

@@

Acknowledging the correct structure of galaxies with intermediate-scale discs is important to properly understand their origin. 
According to the current paradigm of cosmological structure evolution, 
the genesis of massive early-type galaxies is characterized by two distinct phases: ``in-situ'' and ``ex-situ''. 
The first phase takes place in a young Universe (within its first $4~\rm Gyr$), 
when cold gas inflows produced short and intense bursts of star formation 
that created compact and dense conglomerates of stars with high velocity dispersion (e.g.~\citealt{prieto2013}). 
These naked and compact conglomerates, named ``red nuggets'' \citep{damjanov2009}, 
have been observed at high-redshift with half-light sizes of 1--2 kpc \citep{daddi2005,trujillo2006,vandokkum2008}.
In the second phase (last $10~\rm Gyr$), discs and stellar envelopes 
were accreted around these primordial conglomerates and the external parts of today's galaxies assembled on scales of 2--20 kpc 
(e.g.~\citealt{driver2013}). \\
Today's Universe is populated by an abundance of compact, massive spheroids, 
with the same physical properties -- mass and compactness -- as the high-redshift red nuggets \citep{GDS2015}. 
Some of these local compact massive spheroids are encased within a large-scale disc, 
that is to say they are the bulges of some lenticular and spiral galaxies.  
Over the last $10~\rm Gyr$ their spheroids have evolved by growing a relatively flat disc (e.g.~\citealt{pichon2011,danovich2012,stewart2013})
-- rather than a three-dimensional envelope -- 
which has increased the galaxy size but preserved the bulge compactness. 
Of course some lenticular/ES galaxies may have been built from mergers (e.g.~\citealt{querejeta2015}, and references therein). 
The other compact massive spheroids of today's Universe belong to some galaxies with intermediate-scale discs. 
Indeed, Mrk 1216, NGC 1271, NGC 1277, NGC 1332, and NGC 3115 are all local compact intermediate-scale disc galaxies 
with purely old ($>10~\rm Gyr$) stellar populations. 
These galaxies have undergone the lowest degree of disc growth. \\
In addition to the observational clues as to the actual physical components in galaxies with intermediate-scale discs, 
one can reason on other grounds as to why these compact galaxies are not comprised of an inner bulge 
plus large-scale disc plus outer envelope. 
If they were such three-component systems, then one would have two possibilities. 
The first possibility is that these galaxies were already fully assembled $10~\rm Gyr$ ago; 
this would explain their old stellar populations, 
but it would also imply that their discs and envelopes had already formed during the first $4~\rm Gyr$ of the Universe, 
in disagreement with the current cosmological picture. 
The second possibility is that only their inner bulges (with sizes of 0.1--0.2 kpc, 
according to past decompositions) originated in the first $4~\rm Gyr$ 
and they subsequently accreted a substantial disc and envelope. 
If this was correct, then we would observe high-redshift, star-like, naked bulges with stellar masses 
within a factor of a few times the currently observed red nuggets but sizes which are $10$ times smaller. 
However, a dramatically different expectation is reached 
if one considers these galaxies today as spheroid-dominated systems with an intermediate-scale disc; 
in this case, both the galaxy size and the spheroid size are compact (1--2 kpc). 
This implies that, among the local descendants of the high-redshift red nuggets, 
the compact intermediate-scale disc galaxies have undergone the lowest degree of disc growth. 
That is, the bulk of a compact intermediate-scale disc galaxy quickly assembled ``in-situ'' in a very young Universe 
and experienced very little evolution over the last $10~\rm Gyr$.
